Competing Bandits: The Perils of Exploration under Competition

### 2018-09-06 paper/content/introduction.tex
Minor edit.

We consider a \emph{permanent duopoly} in which both firms start at the same time, as well as \emph{temporary monopoly}: a duopoly with an early entrant. Accordingly, the intensity of competition in the model varies from ``permanent monopoly" (just one firm) to ``early entry" (in the temporary monopoly) to permanent duopoly to ``late entry" (temporary monopoly from the incumbent's perspective). We find that a ``greedy algorithm" that does not explicitly explore is most beneficial under duopoly, and even more so under ``late entry". This algorithm also prevails under monopoly, simply because it tends to be easier to deploy. Whereas a temporary monopoly incentivizes more advanced exploration algorithms that perform better in the long run. The disincentives to explore under duopoly arise entirely because of ``reputational costs", rather than R\&D costs (which are absent from our model, aside from the tie-breaking).

>>>>

We consider a \emph{permanent duopoly} in which both firms start at the same time, as well as \emph{temporary monopoly}: a duopoly with an early entrant. Accordingly, the intensity of competition in the model varies from ``permanent monopoly" (just one firm) to ``early entry" (in the temporary monopoly) to permanent duopoly to ``late entry" (temporary monopoly from the incumbent's perspective). We find that a ``greedy algorithm" that does not explicitly explore is most beneficial under duopoly, and even more so under ``late entry". This algorithm also prevails under monopoly, simply because it tends to be easier to deploy. Whereas a temporary monopoly incentivizes more advanced exploration algorithms that perform better in the long run. The disincentives to explore under duopoly arise entirely because of ``reputational costs", rather than R\&D costs (which are absent from our model).
